Algorithms for Longest Common Extensions

### 2011-07-18 doc/report.tex
m

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.4\textwidth,page=1]{ladder.pdf}
        \includegraphics[width=0.4\textwidth,page=2]{ladder.pdf}
    \end{center}
    \caption{\label{fig:ladder-ds} Ladders of a tree before and after their length is doubled. A \proc{LadderLce} string $s$ for this ladder decomposition is $s=abc|ade|f|ghijkl|hno|m$, where the splits between ladders are marked with a vertical line.}
\end{figure}

The \proc{LadderLce} data structure consists of the following:
\begin{itemize}
\item An input tree $T$ with a ladder decomposition.
\item A strings $s$, which is a concatenation of ladder labels for each ladder in $T$, where a ladder label for is $\zlabel(p)$, where $p$ is the path from the first node in the ladder to the last node in the ladder. \pref{fig:ladder-ds} shows an example of $s$.
\item For a node $u$, $\zindex(u)$ is an index in $s$ within the ladder label of $u$'s ladder, where $\zlabel(u)$ is stored.
\item Data structures for constant time LA on $T$ and constant time LCE on $s$.
\end{itemize}

@@

The \proc{LadderLce} query starts with $v=0$ and repeats the following:
\begin{enumerate}
\item Stop when $v = e_i$ or $v = e_j$ and return $v$.
\item Find $m_i = \zlength(p_i[v\twodots e_i])/2$ and $i = \zindex(p_i[v+m_i]) - m_i + 1$.
\fixme{afrunding}
\item Find $m_j = \zlength(p_j[v\twodots e_j])/2$ and $j = \zindex(p_j[v+m_j]) - m_j + 1$.
\item Find $v' = \min\{LCE_s(i,j),m_i,m_j\}$
\item Increment $v$ by $v'$.
\item Stop if $v' < \min\{m_i,m_j\}$ and return $v$.
\end{enumerate}

\begin{lemma}
The \proc{LadderLce} query finds the correct LCE value.
\end{lemma}
\begin{proof}
In step two, $i$ refers to a position in $p_i[v+m_i]$'s ladder, because the height of $p_i[v+m_i]$ is at least $m_i$. Therefore $s[i\twodots i+m_i-1] = \zlabel(p_i[v\twodots v+m_i])$, and similarly $s[j\twodots j+m_i-1] = \zlabel(p_j[v\twodots v+m_j])$.

>>>>

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.4\textwidth,page=1]{ladder.pdf}
        \includegraphics[width=0.4\textwidth,page=2]{ladder.pdf}
    \end{center}
    \caption{\label{fig:ladder-ds} Ladders of a tree before and after their length is doubled. A \proc{LadderLce} string $s$ for this ladder decomposition is $s=abc|ade|df|ghijkl|ghno|jm$, where the splits between ladders are marked with a vertical line.}
\end{figure}

The \proc{LadderLce} data structure consists of the following:
\begin{itemize}
\item An input tree $T$ with a ladder decomposition.
\item A strings $s$, which is a concatenation of ladder labels of each ladder in $T$, where the label of a ladder is the concatenation of labels of each node in the ladder, ordered ascending by the depth of the nodes. \pref{fig:ladder-ds} shows an example of $s$.
\item For a node $u$, $\zindex(u)$ is an index in $s$ within the ladder label of $u$'s ladder, where $\zlabel(u)$ is stored.
\item Data structures for constant time LA on $T$ and constant time LCE on $s$.
\end{itemize}

@@

The \proc{LadderLce} query starts with $v=0$ and repeats the following:
\begin{enumerate}
\item Stop when $v = e_i$ or $v = e_j$ and return $v$.
\item Find $m_i = \lceil\zlength(p_i[v\twodots e_i])/2\rceil$ and $i = \zindex(p_i[v+m_i]) - m_i + 1$.
\fixme{afrunding}
\item Find $m_j = \lceil\zlength(p_j[v\twodots e_j])/2\rceil$ and $j = \zindex(p_j[v+m_j]) - m_j + 1$.
\item Find $v' = \min\{LCE_s(i,j),m_i,m_j\}$
\item Increment $v$ by $v'$.
\item Stop if $v' < \min\{m_i,m_j\}$ and return $v$.
\end{enumerate}

\begin{lemma}
The \proc{LadderLce} query finds the correct LCE value.
\end{lemma}
\begin{proof}
In step two, $i$ refers to a position in $p_i[v+m_i]$'s ladder, because the height of $p_i[v+m_i]$ is at least $m_i-1$. Therefore $s[i\twodots i+m_i-1] = \zlabel(p_i[v\twodots v+m_i])$, and similarly $s[j\twodots j+m_i-1] = \zlabel(p_j[v\twodots v+m_j])$.
